Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-23 paper/paper.tex
Fix valuable occurrences

\begin{abstract}
Issue tracking systems have become the defacto standard for tracking work items in 
software projects - they guide engineers towards better planning and 
managing their progress throughout complex projects. However, there
are few studies that investigate what makes for a high quality,
valuable ticket. This can lead to multiple issues in a company, such as 
increased communication friction between developers and end users filing bug
reports, as well as increased overall costs due to waste of development effort. 
In this research paper, we present our findings after 
investigating a large number of variables surrounding software tickets.
Our results show that the presence and type of attachments,
comments complexity, summary and description complexity, presence of stack traces, presence
of steps to reproduce, grammar correctness scores, as well as sentiment can significantly influence 
the quality of the ticket. We supply one of the largest dataset statistically 
analysed in this particular field, as well as state-of-the-art sentiment and grammar correctness analyses.
\end{abstract}

@@

Therefore, there is a need in the community to find the answer to what makes for a high quality, valuable software ticket 
that would improve the overall performance of the development team and, inherently, the company. Considering the many fields of 
a ticket, there are numerous elements that could influence its quality, such as the presence of stack traces.

@@

The study of Bettenburg et al. \cite{bettenburg2008makes} showed what 
makes for a valuable bug report through qualitative analysis. 
After conducting interviews with over 450 developers, Bettenburg et al. concluded that one of the main factors
behind a quality ticket is grammar correctness in summary and description. Another
aspect which was flagged as helpful by the interviewees was the presence of stack 
traces and steps to reproduce in tickets. A further contribution brought by the
authors to the community is the creation of a tool called Cuezilla which is able 
to automatically predict the quality of a bug report with an accuracy of around 40\%.

@@

The work of Just et al. \cite{just2008towards} examines a rather different aspect
of quality in tickets - they are investigating the quality of the underlying issue 
tracking systems instead. 
After running a survey on 175 developers from Eclipse, Apache and Mozilla,
the authors applied a card sort in order to organize the comments into hierarchies to 
identify common patterns. Their findings can be summarized in the following top seven
suggestions:
  \begin{itemize}
    \item create differentiation between bug report difficulty levels between 
    novices and experiences reporters;
    \item encourage users to input as much information as possible;
    \item add ability to merge tickets when needed;
    \item recognise and reward valuable bug reporters;
    \item integrate reputation into user profiles to mark experienced reporters;
    \item to be able to easily and expressively search through tickets.
  \end{itemize}

Having discussed about various factors that can influence the quality in software tickets, 
we also need to take into account how can we apply this knowledge to solving the issue of 
poor design in issue tracking systems and how the ticket creation process could be improved. 
The study conducted by Lamkanfi et al. \cite{lamkanfi2010predicting} looks at this aspect and
shows how issue tracking systems could be extended in order to automatically generate the severity 
of a ticket (e.g. assign story points to a Jira issue). The authors conducted their research on the Mozilla,
GNOME and Eclipse and projects and split their approach into four steps: extract and organize tickets, 
pre-process tickets (i.e. tokenization, stop word removal and stemming), train the classifier on two datasets 
of tickets - 70\% training and 30\% evaluation and apply the trained classifier on the evaluation set.
The conclusions they drew from running the evaluation process were rather 
interesting:
  \begin{itemize}
    \item terms such as segfault, deadlock, crash, hand or memory typically indicate
      a severe bug;
    \item when analyzing the textual description they found that using simple
      one line summaries resulted in less false positives and increased precision
      levels;
    \item the classifier needs a large number of tickets in order to predict correctly;
    \item depending on how well a software project is modularised, one can 
      use a predictor per module rather than a universal one.
  \end{itemize}

@@

Sentiment analysis is a technique of employing Machine Learning algorithms in order to infer a sentiment 
score from textual information. These algorithms need to be trained on very large data sets in order to 
produce valuable results. Moreover, we would have also needed an already annotated data set, which means 
a number of strings where we compute the score by hand given a mathematical formula we define. Even though 
there are open source libraries that can help with creating and employing the algorithms, such as TensorFlow, 
we would still have needed tickets where we defined what is meant by positive/negative tickets, as well as
manually computing the scores for a large range of them. Therefore, we ended using a third party API - Google 
Cloud Platform Natural Language Processing, considered the best such service at the moment. This API returns 
a score between -1 (most negative) and +1 (most positive) for any text encoded in the HTTP request.

@@

We strongly believe that having a positive sentiment score for tickets is valuable for absolutely everyone: the company
behind the projects sees increased overall performance and productivity, developers feel better working in the team or
on that specific tool and reporters will be more willing to contribute in the future with other tickets.

>>>>

\begin{abstract}
Issue tracking systems have become the defacto standard for tracking work items in 
software projects - they guide engineers towards better planning and 
managing their progress throughout complex projects. However, there
are few studies that investigate what makes for a high quality ticket. This can lead to 
multiple issues in a company, such as increased communication friction between developers and end users filing bug
reports, as well as increased overall costs due to waste of development effort. 
In this research paper, we present our findings after 
investigating a large number of variables surrounding software tickets.
Our results show that the presence and type of attachments,
comments complexity, summary and description complexity, presence of stack traces, presence
of steps to reproduce, grammar correctness scores, as well as sentiment can significantly influence 
the quality of the ticket. We supply one of the largest dataset statistically 
analysed in this particular field, as well as state-of-the-art sentiment and grammar correctness analyses.
\end{abstract}

@@

Therefore, there is a need in the community to find the answer to what makes for a high quality software ticket 
that would improve the overall performance of the development team and, inherently, the company. Considering the many fields of 
a ticket, there are numerous elements that could influence its quality, such as the presence of stack traces.

@@

The study of Bettenburg et al. \cite{bettenburg2008makes} showed what 
makes for a high quality bug report through qualitative analysis. 
After conducting interviews with over 450 developers, Bettenburg et al. concluded that one of the main factors
behind a quality ticket is grammar correctness in summary and description. Another
aspect which was flagged as helpful by the interviewees was the presence of stack 
traces and steps to reproduce in tickets. A further contribution brought by the
authors to the community is the creation of a tool called Cuezilla which is able 
to automatically predict the quality of a bug report with an accuracy of around 40\%.

@@

The work of Just et al. \cite{just2008towards} examines a rather different aspect
of quality in tickets - they are investigating the quality of the underlying issue 
tracking systems instead. 
After running a survey on 175 developers from Eclipse, Apache and Mozilla,
the authors applied a card sort in order to organize the comments into hierarchies to 
identify common patterns. Their findings can be summarized in the following top seven
suggestions: create differentiation between bug report difficulty levels between 
novices and experiences reporters, encourage users to input as much information as possible, 
add ability to merge tickets when needed, recognise and reward valuable bug reporters, integrate 
reputation into user profiles to mark experienced reporters and ensure the ability to expressively search through tickets.

Having discussed about various factors that can influence the quality in software tickets, 
we also need to take into account how can we apply this knowledge to solving the issue of 
poor design in issue tracking systems and how the ticket creation process could be improved. 
The study conducted by Lamkanfi et al. \cite{lamkanfi2010predicting} looks at this aspect and
shows how issue tracking systems could be extended in order to automatically generate the severity 
of a ticket (e.g. assign story points to a Jira issue). The authors conducted their research on the Mozilla,
GNOME and Eclipse and projects and split their approach into four steps: extract and organize tickets, 
pre-process tickets (i.e. tokenization, stop word removal and stemming), train the classifier on two datasets 
of tickets - 70\% training and 30\% evaluation and apply the trained classifier on the evaluation set.
The conclusions they drew from running the evaluation process were rather 
interesting: terms such as segfault, deadlock, crash, hand or memory typically indicate
a severe bug, when analyzing the textual description they found that using simple
one line summaries resulted in less false positives and increased precision
levels, the classifier needs a large number of tickets in order to predict correctly, 
depending on how well a software project is modularised and, lastly, one can 
use a predictor per module rather than a universal one.

@@

Sentiment analysis is a technique of employing Machine Learning algorithms in order to infer a sentiment 
score from textual information. These algorithms need to be trained on very large data sets in order to 
produce valid results. Moreover, we would have also needed an already annotated data set, which means 
a number of strings where we compute the score by hand given a mathematical formula we define. Even though 
there are open source libraries that can help with creating and employing the algorithms, such as TensorFlow, 
we would still have needed tickets where we defined what is meant by positive/negative tickets, as well as
manually computing the scores for a large range of them. Therefore, we ended using a third party API - Google 
Cloud Platform Natural Language Processing, considered the best such service at the moment. This API returns 
a score between -1 (most negative) and +1 (most positive) for any text encoded in the HTTP request.

@@

We strongly believe that having a positive sentiment score for tickets is beneficial for everyone: the company
behind the projects sees increased overall performance and productivity, developers feel better working in the team or
on that specific tool and reporters will be more willing to contribute in the future with other tickets.
